Hardware-accelerated Rendering of Intersecting Volumes using Boolean Operations

### 2013-06-03 paper.tex
Say 'generally require' instead of 'can require' in abstract

% ========
% Abstract
% ========
\begin{abstract}
Rendering intersecting volumes is problematic because the renderer must
alternate between sampling from each volume to achieve the correct blending.
Methods for rendering an arbitrary number of intersecting volumes on the GPU
have been developed, but they can require a large amount of geometry to be
created every frame, or may be difficult or time-consuming to implement.  This
paper investigates whether using familiar Boolean operations may be faster or
easier to implement in the simple case where two axis-aligned volumes intersect.
\end{abstract}

>>>>

% ========
% Abstract
% ========
\begin{abstract}
Rendering intersecting volumes is problematic because the renderer must
alternate between sampling from each volume to achieve the correct blending.
Methods for rendering an arbitrary number of intersecting volumes using hardware
acceleration have been developed, but they generally require a large amount of
geometry to be created every frame, or may be difficult or time-consuming to
implement.  This paper investigates whether using familiar Boolean operations
may be faster or easier to implement in the simple case where two axis-aligned
volumes intersect.
\end{abstract}
